####REPRODUCIBLE RESEARCH ASSIGNMENT 1####
###1.LOAD THE DATA###
```{r, echo FALSE}
library(ggplot2)
library(scales)
library(Hmisc)
activity <- read.csv("C:/Users/suparnapal2000/Downloads/repdata_data_activity/activity.csv")
```
###2.MEAN TOTAL STEPS TAKEN PER DAY###
```{r}
stepsByDay <- tapply(activity$steps, activity$date, sum, na.rm = T)
```
###1.HISTOGRAM OF TOTAL NUMBER OF STEPS TAKEN PER DAY###
```{r}
library(ggplot2)
qplot(stepsByDay, xlab = "Total steps per day", ylab = "Frequency")
```
###MEAN AND MEDIAN OF TOAL STEPS TAKEN PER DAY
```{r}
mean value <- mean(stepsByDay)
median value <- median(stepsByDay)
```
###AVERAGE DAILY ACTIVITY PATTERN###
```{r}
library(ggplot2)
averages <- aggregate(x = list(steps = activity$steps), by = list(interval = activity$interval), FUN = mean, na.rm = T )
ggplot(data = averages, aes(x = interval, y = steps))+ geom_line() + 
  xlab("5-minute interval")+
  ylab("average no of steps taken")
```
###MAXIMUM NO OF STEPS###
```{r}
averages[which.max(averages$steps), ]
```
###MISSING VALUES###
```{r}
missing values <- length(which(is.na(activity$steps)))
```
###NEW DATA SET EQUAL TO ORGINAL DATA BUT WITH MISSING VALUE###
```{r}
activityDataImputed <- activity
activityDataImputed$steps <- impute(activity$steps, fun = mean)
```
###HISTOGRAM OF TOTAL NO OF STES TAKEN EACH DAY WITH IMPUTED VALUE###
```{r}
stepsByDayImputed <- tapply(activityDataImputed$steps,activityDataImputed$date, sum )
qplot(stepsByDayImputed , xlab = "Total steps per day imputed", ylab = "Frequency")
```
###MEAN AND MEDIAN OF IMPUTED VALUE###
```{r}
stepsByDayMeanImputed <- mean(stepsByDayImputed)
stepsByDayMedianImputed <- median(stepsByDayImputed)
```
#### Are there differences in activity patterns between weekdays and weekends?
##### 1. Create a new factor variable in the dataset with two levels ??? ???weekday??? and ???weekend??? indicating whether a given date is a weekday or weekend day.


```{r}
activityDataImputed$dateType <-  ifelse(as.POSIXlt(activityDataImputed$date)$wday %in% c(0,6), 'weekend', 'weekday')
```

##### 2. Panel plot containing a time series plot


```{r}
averagedActivityDataImputed <- aggregate(steps ~ interval + dateType, data=activityDataImputed, mean)
ggplot(averagedActivityDataImputed, aes(interval, steps)) + 
    geom_line() + 
    facet_grid(dateType ~ .) +
    xlab("5-minute interval") + 
    ylab("avarage number of steps")
```

